Automated Lensing Learner - I: An automated Strong Lensing Identification Pipeline

### 2017-03-09 ms.tex
Added relevance of paper to tail end of intro

% Application of constraining mass profiles - large numbers needed.
The application of strong gravitational lensing to constrain the mass
distribution of \todo{early-type galaxies (ETGs)} necessitates large
samples of galaxy-galaxy lensing systems.  The strong lensing
signature... EDITING HERE These systems exhibit a background source
galaxy that the ETG deflects into a partial of full arc shaped
Einstein ring.

@@

>>>>

% Application of constraining mass profiles - large numbers needed.
The application of strong gravitational lensing to constrain the mass
distribution of strong lenses, such as early-type galaxies (ETGs),
necessitates large samples of galaxy-galaxy lensing systems.  The
strong lensing signature directly probes the underlying matter. These
systems exhibit a background source galaxy that the lens galaxy
deflects into a partial of full arc shaped Einstein ring.

@@

%  Relevance of our work
While there has been a recent surge in the use of neural networks
applied to image classification problems, these implementations are
not easily scalable, nor easily accessible to the entire scientific
community.  We present a supervised classification pipeline built with
open source tools, tested on mock HST and LSST data.  Results are
reproducible on personal computers, as both the pipeline and the data
will be publicly distributed.
